Create Walkover of Brief Names

### 2022-04-05 data-cleaning/04-create-walkover-brief-name.Rmd
create walkover for brief names

# data manip
library(tidyverse)
library(fuzzyjoin)

# data
# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization
brief_info <- box_read("936715223606")

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")
```

```{r}
brief_names <- brief_info %>% filter(`Row Type...9` == "Amicus Brief") %>% 
              select(`Amicus Brief`) %>% unique()

briefs_to_match <- amicus %>% select(brief) %>% unique()
```

Currently none of the names of briefs match between these two files.

```{r}
intersect(brief_names[["Amicus Brief"]], briefs_to_match[["brief"]])
```

It looks like the brief names in the file with text for topic modeling are a combination of case names and brief names. I want to remove the case portion and see if they match better with the brief names in the author information data.

1. Make everything lower case
2. Replace all v. with v
3. Remove .docx
4. Remove all text at beginning of string with `text v text. ` or `text v text - `
5. Remove `%2c`
6. Remove all punctuation and spacing

```{r}
#1
briefs_to_match$clean_names <- tolower(briefs_to_match$brief)
brief_names$clean_names <- tolower(brief_names$`Amicus Brief`)

#2
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, 'v\\.', 'v')

#3
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '\\.docx', '')

#4
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '([^v]*v[^\\.]*\\. )|([^v]*v[^-]*- )', '')

#5
briefs_to_match$clean_names <- str_replace(briefs_to_match$clean_names, '%2c', '')

#6
briefs_to_match$clean_names <- str_replace_all(briefs_to_match$clean_names,
                                               '[^[:alnum:]]','')
brief_names$clean_names <- str_replace_all(brief_names$clean_names,
                                               '[^[:alnum:]]','')
```

Sorting by brief name.

```{r}
brief_names <- brief_names[order(brief_names$clean_names),]
briefs_to_match <- briefs_to_match[order(briefs_to_match$clean_names),]
```

After all of the cleaning I was only able to match 268 brief names.

```{r}
join <- brief_names %>% left_join(briefs_to_match, by = c("clean_names"))

table(is.na(join$brief))
```

>>>>

# data manip
library(tidyverse)

# parallel processing
library(R.utils)
library(doParallel)

# data
# regressions/data for Amicus IV regressions/Amicus Author Organization Categorization.xlsx
brief_info <- box_read("936715223606")

# data/processed amicus files/amicus_text_512.csv
amicus <- box_read("937207017356")

# data/author and amicus measures/amicus-level-measures.csv
author_level <- box_read("861296487195")
```

Set the working directory for files to gets IDs for.

```{r}
box_setwd("99209523670")
```

```{r}
# Get the IDs of all the case folders 
case_folders <- box_ls() %>%
  as.data.frame() %>% 
  filter(type == "folder") %>% 
  rename(case = name)

case_folders %>% head(1)
```

For all of the folders, retrieve every file name and ID.

```{r}
# number of cores available
n_cores <- detectCores() - 1
registerDoParallel(n_cores)

# given a df of ids for SC folder, extract names and ids of all files in case folder
# then, save
all_file_names <- function(case_folder_ids) {

  # get info for all files contained in each case folder
  # stored in a list of lists
  cases_ids_list <- mclapply(case_folder_ids$id,
                                box_ls,
                                mc.cores = n_cores)

  # convert to list of df
  cases_ids_list <- map(cases_ids_list, as.data.frame)

  # get name of folder (this is case name)
  cases_ids_list <- lapply(cases_ids_list, function(x) transform(x, case = sub(".*/", "", path)))

  print("Created list of dfs; each element is a case folder")

  # create iterator that will go through list element by element
  it <- iter(cases_ids_list, by = "row")

  # in each case folder, grab the name and id of the decision file
  file_ids <-
    foreach(i = it,
            .combine = rbind,
            .inorder = F) %dopar% {
              i %>%
                filter(grepl("amicus|amici", name, ignore.case = T)) %>%
                select(case, name, id)
            }
  print("Obtained amicus file ids")

  return(file_ids)
}

amicus_file_ids <- all_file_names(case_folders)

doParallel::stopImplicitCluster()
```

Join the different brief names into one dataframe.

```{r}
join_data <- author_level %>% select(id = BoxFileID, name_incorrect = AmicusBrief, CaseId)
join_data$id <- as.character(join_data$id)

join_data2 <- amicus_file_ids %>% select(id, name_correct = name)

data <- left_join(join_data, join_data2, by = c("id"))
```

```{r}
table(is.na(data$name_correct))
```

```{r}
data %>% filter(is.na(name_correct))
```

```{r}
data[data$id == 592236091833,'name_correct'] <- 'Stenberg v Carhart. Amics Brief for Petitioner by Agudath Israel of America.docx'
```

```{r}
check_in_amicus <- amicus %>% left_join(data, by = c('brief' = 'name_correct'))
june_russo_fix <- check_in_amicus %>% filter(is.na(name_incorrect)) %>%
  select(brief) %>% unique()
```

Write to csv

```{r}
box_write(data,
           file_name = "walkover_brief_names.csv",
           dir_id = 145990409196)
```
